\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage[margin=1in]{geometry} % Set margins
\usepackage{hyperref} % For links

\title{CS 348 - Report}
\author{Kegan Allen, Luke Martin, Matteo Pesenti, Angelina Wu, Eric Zhang}
\date{Spring 2024 - Group 21}

\begin{document}

\maketitle

\noindent Link to repository: \href{https://github.com/LukasMartini/CS348Group21Project}{CS348Group21Project}

\section{Project Introduction}

%Poker hand history tracker with bankroll, bet habit vs hand value, etc. information. Social features (posting hand/game history publicly, commenting)

At present, our application will primarily be a central platform for poker players to view, comment on, and make use of their game replays and personal statistics,
as well as those posted publicly by other users. As such, our database will be a repository of game results (play history, betting habits, etc.), loss/ gain
tracking information, and account data. \\

\noindent To accomplish this, we must rely almost entirely on our users. Our focus on game statistics necessarily requires some level of input from clients, 
as obtaining the information directly from popular online poker platforms (PokerStars, etc.) requires technologies that are outside of the scope of this project. 
Since the app will likely stay localized within the group for the duration of this course, the dataset can only be comprised of games that are extractable from public sources
or from our members. However, if we were to deploy, it would include data from anyone with an account. 
Either way, it is our responsibility as a team to be the database administrators.

\section{Choice of Platform}

%- Choice of platform: reactTS, python (flask), postgresql, local machines

Due to the relative variety and complexity of our data, it is needlessly complicated to interact with the database using the commandline.
As such, our user interface will consist of a React-based website supported by a Flask back-end, giving us flexibility in how we manage the database 
while keeping the user experinece simple. For the database, we intend on using Postgresql, so our local machines are our platform of choice.

\section{Group Member Contribution}

All group members participated in the preparation of Milestone 0 equally via writing or editing the report or the "hello world" equivalent.

\end{document}
